Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/advup.tex

Contrary to this discrete action exploration scheme, $\varepsilon$-greedy
exploration is likely to not explore, i.e. to collapse to a deterministic
policy when $\deltat$ goes to $0$. Indeed, one can prove that in a near
continuous deterministic environment, the exploration policy resulting from
applying $\varepsilon$-greedy exploration to a constant exploitation policy
converges to a determinist policy as $\deltat$ goes to $0$. More precisely, let
$(a_\deltat)$ be a sequence of i.i.d. actions of distribution drawn from $p_A$, (for instance
the sequence of actions generated by $\varepsilon$-greedy exploration on a
constant policy). Then, as $\deltat$ goes to $0$, trajectories generated by
interacting with the environment using the $a$'s converge to solutions of
\begin{equation}
	ds_t = \E_{a\sim p_A}\left[F(s_t, a)\right]dt
\end{equation}
where the expectation cancels the exploration noise. The proof is given in the
supplementary material. \TODO{Is there a stronger theorm? Should we talk more about that?}

>>>>

On the other hand,
$\varepsilon$-greedy
exploration is likely \emph{not} to explore, i.e. to collapse to a deterministic
policy, when $\deltat$ goes to $0$.
% Indeed, in a
% near-continuous deterministic environment, %the exploration policy resulting from
% applying $\varepsilon$-greedy exploration to a given exploitation policy
% converges to a determinist policy as $\deltat$ goes to $0$.
Intuitively,
with very small $\deltat$, changing the action at random every $\deltat$ time
step just averages out the randomness due to the law of large numbers.
More precisely, let
$(a_\deltat)$ be a sequence of i.i.d.\ actions drawn from a distribution $p_A$, (for instance
the sequence of actions generated by $\varepsilon$-greedy exploration on a
fixed policy) in a near-continuous environment. Then, as $\deltat$ goes
to $0$, the trajectories generated by
this policy tend to solutions of the deterministic equation
\begin{equation}
	ds_t/dt  = \E_{a\sim p_A}\left[F(s_t, a)\right]
\end{equation}
where the expectation cancels the exploration noise. The proof is given in the
supplementary material. \TODO{Is there a stronger theorm? Should we talk more about that?}
